Viscous Transport in Eroding Porous Media

### 2019-07-16 docs/transport/erosion_transport.tex
add new fig in transport paper

@@

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/anomalous_diffusion20d}
\caption{\label{fig:Eroding20anomalous} The analysis of anomalous diffusion in
 20 nearly touching bodies with respect to two prosities. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{50 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\color{red}
The second nearly touching bodies case is 50 bodies in a Hagen-Poiseuille flow.
}

>>>>

\todo[inline]{gap size growth as a function of time}

@@

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/anomalous_diffusion20d_new}
\caption{\label{fig:Eroding20anomalous} The analysis of anomalous diffusion in
 20 nearly touching bodies with respect to six porosities. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{50 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\color{red}
The second nearly touching bodies case is 50 bodies in a Hagen-Poiseuille flow.
}
